\large How resource abundance and resource stochasticity affect organisms' range sizes

### 2025-02-18 writing/appendix-A-concepts-and-definitions.Rmd
submitting response to reviews

---
title: \large How resource abundance and stochasticity affect organisms' range sizes
subtitle: "Appendix A: Concepts and definitions"
# author:
#   - name: Stefano Mezzini
#     email: stefano.mezzini@ubc.ca
#     institute: [braes, biol]
#   - name: Chris H. Fleming
#     institute: [ucf, smith]
#   - name: E. Patrícia Medici
#     institute: [tapir, iucn, escas]
#   - name: Michael J. Noonan
#     email: michael.noonan@ubc.ca
#     institute: [braes, biol, cmps]
# institute:
#   - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
#   - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
#   - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
#   - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
indent: true
header-includes:
    - \renewcommand{\figurename}{Figure A\!\!} # for "Figure Ax".
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
    # latex_engine: xelatex # for sigma characters in figure
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

>>>>

---
title: \large How resource abundance and resource stochasticity affect organisms' range sizes
subtitle: "Appendix A: Concepts and definitions"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [braes, biol]
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [braes, biol, cmps]
institute:
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
indent: true
header-includes:
    - \renewcommand{\figurename}{Figure A\!\!} # for "Figure Ax".
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
    # latex_engine: xelatex # for sigma characters in figure
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

### 2025-02-18 writing/appendix-B-simulations.Rmd
submitting response to reviews

---
title: \large How resource abundance and stochasticity affect organisms' range sizes
subtitle: "Appendix B: Simulations"
# author:
#   - name: Stefano Mezzini
#     email: stefano.mezzini@ubc.ca
#     institute: [biol, braes]
#   - name: Chris H. Fleming
#     institute: [ucf, smith]
#   - name: E. Patrícia Medici
#     institute: [tapir, iucn, escas]
#   - name: Michael J. Noonan
#     email: michael.noonan@ubc.ca
#     institute: [biol, braes, cmps]
# institute:
#   - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
#   - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
#   - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
#   - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
header-includes:
    - \renewcommand{\figurename}{Figure B\!\!} # for "Figure Bx."
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: \large How resource abundance and resource stochasticity affect organisms' range sizes
subtitle: "Appendix B: Simulations"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [biol, braes]
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [biol, braes, cmps]
institute:
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
header-includes:
    - \renewcommand{\figurename}{Figure B\!\!} # for "Figure Bx."
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
editor_options: 
  chunk_output_type: console
---

### 2025-02-18 writing/appendix-C-empirical-modeling.Rmd
submitting response to reviews

---
title: \large How resource abundance and stochasticity affect organisms' range sizes
subtitle: "Appendix C: Empirical modeling"
# author:
#   - name: Stefano Mezzini
#     email: stefano.mezzini@ubc.ca
#     institute: [biol, braes]
#   - name: Chris H. Fleming
#     institute: [ucf, smith]
#   - name: E. Patrícia Medici
#     institute: [tapir, iucn, escas]
#   - name: Michael J. Noonan
#     email: michael.noonan@ubc.ca
#     institute: [biol, braes, cmps]
# institute:
#   - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
#   - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
#   - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
#   - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
#   - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
#   - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
header-includes:
    - \renewcommand{\figurename}{Figure C\!\!} # for "Figure Sx.
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    -  \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex # for unicode characters
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    toc: false
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: \large How resource abundance and resource stochasticity affect organisms' range sizes
subtitle: "Appendix C: Empirical modeling"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [biol, braes]
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [biol, braes, cmps]
institute:
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
fontsize: 12pt
header-includes:
    - \renewcommand{\figurename}{Figure C\!\!} # for "Figure Sx.
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    -  \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex # for unicode characters
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    toc: false
editor_options: 
  chunk_output_type: console
---

### 2025-02-18 writing/manuscript.Rmd
submitting response to reviews

---
title: \large How resource abundance and resource stochasticity affect organisms' range sizes
author:
  - name: Stefano Mezzini
    institute: [braes, biol]
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [braes, biol, cmps]
    correspondence: "yes"
institute:
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'movement-ecology.csl'
fontsize: 12pt
indent: true
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage{indentfirst} # for indenting first line of each paragraph
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{wrapfig} # for wrapping text around figures
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font={scriptsize, doublespacing}, labelfont=bf, aboveskip=4pt, belowskip=-15pt}
    - \usepackage{hanging} # for hanging indents in references
    - \usepackage[left]{lineno} # for line numbers
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
#   bookdown::word_document2:
#     pandoc_args:
# # https://github.com/pandoc/lua-filters/blob/master/author-info-blocks/README.md
#       - '--lua-filter=scholarly-metadata.lua'
#       - '--lua-filter=author-info-blocks.lua'
#     toc: false
#     number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex # @reed_frequency_2003 has character \U0308
    pandoc_args:
# https://github.com/pandoc/lua-filters/blob/master/author-info-blocks/README.md
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    toc: false
    number_sections: false
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: \large How resource abundance and resource stochasticity affect organisms' range sizes
author:
  - name: Stefano Mezzini
    institute: [braes, biol]
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [braes, biol, cmps]
    correspondence: "yes"
institute:
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'movement-ecology.csl'
fontsize: 12pt
indent: true
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage{indentfirst} # for indenting first line of each paragraph
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{wrapfig} # for wrapping text around figures
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font={scriptsize, doublespacing}, labelfont=bf, aboveskip=4pt, belowskip=-15pt}
    - \usepackage{hanging} # for hanging indents in references
    - \usepackage[left]{lineno} # for line numbers
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
#   bookdown::word_document2:
#     pandoc_args:
# # https://github.com/pandoc/lua-filters/blob/master/author-info-blocks/README.md
#       - '--lua-filter=scholarly-metadata.lua'
#       - '--lua-filter=author-info-blocks.lua'
#     toc: false
#     number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex # @reed_frequency_2003 has character \U0308
    pandoc_args:
# https://github.com/pandoc/lua-filters/blob/master/author-info-blocks/README.md
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    toc: false
    number_sections: false
    keep_tex: true
editor_options: 
  chunk_output_type: console
---
